Stats Project 2

### 2022-12-12 article.Rmd
update article

To improve the quality of our model, we decided to remove outliers as analaysis shows marginal improvements to R\^2 and marginal deterioration to the Press Statistic. We notice the following outliers:

@@

@@

Mean(SalePrice) = b0 + b1(OverallQual) + b2(OverallCond) + b3(YearBuilt) + b4(

>>>>

To improve the quality of our model, we look at outliers as analaysis shows marginal improvements to R\^2 and marginal deterioration to the Press Statistic. We notice the following outliers:

@@

However, removing them did not improve the model, so we decided to leave them in.

@@

Mean(SalePrice) = b0 + b1(LotArea) + b2(OverallCond) + b3(YearBuilt) + b4(YearRemodAdd) + b5(BsmtFinSF1) + b6(BsmtFinSF2) + b7(BsmtFinSF3) + b8(GrLivArea) + b9(BsmtFullBath) + b10(KitchenAbvGr) + b11(Fireplaces) + b12(GarageArea) + b13(WoodDeckSF) + b14(EnclosedPorch) + b15(ScreenPorch) + b16(PoolArea) + b17(YrSold)
